---
title: "Authoring with Code"
message: FALSE
warning: FALSE
format:
  html:
    df-print: paged
    lightbox: auto
---

# GitHub Copilot

RStudio has a built-in connection to GitHub's Copilot. Go to Tools \> Global Options \> Code \> Copilot to enable it.

## Use Copilot to create a Mermaid diagram

[Diagrams](https://quarto.org/docs/authoring/diagrams.html)

# Data Frames

A great way to display data frames is by using `df-print: paged` in the YAML. 

```yaml
---
title: "Document"
format: 
   html:
     df-print: paged
---
```

For more details, see the [Quarto documentation](https://quarto.org/docs/computations/r.html#data-frames).

Here's an example with the Palmer Penguins dataset:

```{r}
#| message: FALSE
library(palmerpenguins)
penguins
```

For more advanced tables, including search and filtering, see the [DT (DataTables) package](https://rstudio.github.io/DT/).

# Code output locations

A very useful feature of Quarto is the ability to control where code output appears. This can be used to create a variety of different layouts and formats. A particularly useful option is to place figures in the margin, which can be done using the `column: margin` option in the code chunk.

```{r}
#| echo: fenced
#| label: fig-penguins
#| fig-cap: "Penguin bill length vs. body mass"
#| column: margin

library(ggplot2)
ggplot(penguins, aes(x = bill_length_mm, y = body_mass_g, color = species)) + 
  geom_point() +
  geom_smooth() +
  theme(legend.position = 'bottom')
```

For more details, see [Margin Content](https://quarto.org/docs/authoring/article-layout.html#margin-content) in the Quarto documentation.

# Lightbox figures

Figures in the margins might be difficult to read, but you can use the `lightbox: auto` option in the YAML to make them clickable and viewable in a larger format. Click on the figure in the margin to see this in action.

```yaml
---
lightbox: auto
---
```

See the [Lightbox Figures](https://quarto.org/docs/output-formats/html-lightbox-figures.html) section of the Quarto documentation for more details.

# Code Annotation

```{r}
#| echo: fenced
library(tidyverse)
library(palmerpenguins)
penguins |>                                      # <1>
  mutate(                                        # <2>
    bill_ratio = bill_depth_mm / bill_length_mm, # <2>
    bill_area  = bill_depth_mm * bill_length_mm  # <2>
  )                                              # <2>
```

1. Take `penguins`, and then,
2. add new columns for the bill ratio and bill area.

See [Code Annotation](https://quarto.org/docs/authoring/code-annotation.html) for more details.

# Code Listings

[Code Listings](https://quarto.org/docs/authoring/cross-references.html#code-listings)

# Conditional Content

[Conditional Content](https://quarto.org/docs/authoring/conditional.html)
